Validation failed EVT

### 2022-07-26 analysis/article-results.Rmd
Start of cleanup for proper interaction-by-cohort

---
title: "Article results"
author: "E. F. Bonneville"
date: "`r Sys.setenv(LANG = 'en_US.UTF-8'); format(Sys.Date(), '%d %B %Y')`"
output: 
  html_document:
    df_print: kable
    toc: yes
    toc_float: 
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

@@

# Load libraries for knitting
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)
library(rms)
library(glmnet)
```

@@

# Summaries of all continuous variables
kableone(table_one$ContTable, nonnormal = TRUE)
```

@@

```{r table-one-categ}
# Summaries of all categorical variables
kableone(table_one$CatTable)
```

@@

```{r miss-dat-summ}
# Seperate datasets
dat_develop <- subset(x = dat_to_impute, select = -dataset, subset = (dataset == "develop"))
dat_valid <- subset(x = dat_to_impute, select = -dataset, subset = (dataset == "valid"))

# Check proportion of complete cases in target analysis (quite good, compare results)

# Development
mean(complete.cases(dat_develop[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

# Validation
mean(complete.cases(dat_valid[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

# Combined
mean(complete.cases(dat_to_impute[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
naniar::gg_miss_upset(dat_valid, nsets = 10)
naniar::gg_miss_upset(dat_develop, nsets = 10)
```

@@

# Print penalied model coefficients
knitr::kable(data.frame(mod_coefs))
```

@@

psfmi::pool_auc(auc_df$auc, sqrt(auc_df$var_auc), nimp = max(as.numeric(auc_df$.imp)))

# Get cal slope and intercept
split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ lp_valid, family = binomial, data = .x)) |> 
  mice::pool() |> 
  summary()

split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ offset(lp_valid), family = binomial, data = .x)) |> 
  mice::pool() |> 
  summary()

>>>>

---
title: "Validation failed EVT"
author: "E. F. Bonneville"
date: "`r Sys.setenv(LANG = 'en_US.UTF-8'); format(Sys.Date(), '%d %B %Y')`"
output: 
  html_document:
    df_print: kable
    toc: yes
    toc_float: 
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

@@

# Load libraries for knitting
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)
library(rms)
library(glmnet)
library(DT)
```

@@

# Summaries of all continuous variables
invisible(
  capture.output(
    tab_contin <- print(
      x = table_one$ContTable, 
      nonnormal = TRUE, 
      noSpaces = TRUE
    )
  )
)

#https://stackoverflow.com/questions/50039186/add-download-buttons-in-dtrenderdatatable
DT::datatable(
  tab_contin,
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

```{r table-one-categ}
# Summaries of all categorical variables
invisible(
  capture.output(
    tab_cat <- print(
      x = table_one$CatTable, 
      nonnormal = TRUE, 
      noSpaces = TRUE
    )
  )
)

DT::datatable(
  tab_cat,
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

```{r cca-check}
# Seperate datasets
dat_develop <- subset(x = dat_to_impute, select = -dataset, subset = (dataset == "develop"))

dat_valid <- subset(x = dat_to_impute, select = -dataset, subset = (dataset == "valid"))

# Development
prop_cca_dev <- mean(complete.cases(dat_develop[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

# Validation
prop_cca_valid <- mean(complete.cases(dat_valid[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

# Combined
prop_cca_comb <- mean(complete.cases(dat_to_impute[, c("Mc_FailedFemoralApproach", candidate_predictors)]))
```

Complete-case analysis (using predictors in the prediction model) results in:

- `r paste0(round(prop_cca_dev * 100, 2), " %")` complete cases in the development data
- `r paste0(round(prop_cca_valid * 100, 2), " %")` complete cases in the validation data
- `r paste0(round(prop_cca_comb * 100, 2), " %")` complete cases in the combined data

```{r miss-dat-summ}
# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
naniar::gg_miss_upset(dat_valid, nsets = 10)
naniar::gg_miss_upset(dat_develop, nsets = 10)
```

@@

# Print penalised model coefficients
#knitr::kable(data.frame(mod_coefs))
DT::datatable(
  data.frame(round(mod_coefs, digits = 3)),
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

auc_ext <- psfmi::pool_auc(
  est_auc = auc_df$auc,
  est_se = sqrt(auc_df$var_auc),
  nimp = max(as.numeric(auc_df$.imp))
)

# Get cal slope and intercept
cal_slope_ext <- split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ lp_valid, family = binomial, data = .x)) |> 
  mice::pool() |> 
  summary(conf.int = TRUE)

cal_int_ext <- split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ offset(lp_valid), family = binomial, data = .x)) |> 
  mice::pool() |> 
  summary(conf.int = TRUE)

int_ext <- with(
  cal_int_ext, 
  paste0(
    round(estimate, 3), " [",
    round(`2.5 %`, 3), ", ",
    round(`97.5 %`, 3), "]"
  )
)

slope_ext <- with(
  cal_slope_ext[2, ], 
  paste0(
    round(estimate, 3), " [",
    round(`2.5 %`, 3), ", ",
    round(`97.5 %`, 3), "]"
  )
)

auc_ext_bis <- with(
  as.data.frame(auc_ext),
  paste0(
    round(`C-statistic`, 3), " [",
    round(`95% Low`, 3), ", ",
    round(`95% Up`, 3), "]"
  )
)

rbind.data.frame(
  cbind.data.frame("measure" = "auc", "value" = auc_ext_bis),
  cbind.data.frame("measure" = "intercept", "value" = int_ext),
  cbind.data.frame("measure" = "slope", "value" = slope_ext)
)
